Faithful Variable Screening for High-Dimensional Convex Regression

### 2014-09-10 tex/scam/appendix.tex
new plots

The middle term can be bounded with the fact that $\|f^*_k - \bar{f}^*_k \|_\infty \leq 2B$.

@@

By Corollary~\ref{cor:convexbracket_ln}, with probability at least $1-\delta$, each bracketing pair $(h_U, h_L)$ is close in $L_1(P_n)$ norm, i.e., for all $(h_U, h_L)$, 
$\frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i) | \leq 2 \epsilon + sB \sqrt{ \frac{sK^{**}(2sbB
)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$, where we assumed that condition~\ref{cond:simplify_covering_number} holds.

@@

We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{ \frac{sK^{**}(2sbBc_u)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. \\

As proved before, the event $\| w \|_\infty \leq \sigma \sqrt{ 2\log \frac{2n}{\delta}}$ has probability at most $1-\delta$. We take an union bound between this event and the event that for all $h$, $\frac{1}{n}\sum_{i=1}^n | h(X_i) - h_L(X_i)|$ is small:
\[
|\langle w, h - h_L\rangle_n| \leq \| w \|_\infty \frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq
  \sigma \sqrt{2 \log \frac{4n}{\delta}} \left( \epsilon + \epsilon_{n,2\delta} \right)
\]

By another property of subgaussian random variables, for any fixed vector $h_L = (h_L(X_1),...,h_L(X_n))$, with probability at least $1-\delta$, $|\langle w, h_L \rangle_n | \leq \| h_L \|_n \sigma \sqrt{ \frac{2}{n} \log \frac{2}{\delta} }$. Union bound again, we have that 
$\sup_{h_L} |\langle w, h_L \rangle| \leq sB \sigma \sqrt{ \frac{2}{n}\log \frac{2 N_{[]}}{\delta}}$.

Putting this together, we have that
\begin{align*}
|\langle w, h \rangle_n | &\leq | \langle w, h_L\rangle_n| + |\langle w, h - h_L\rangle_n|\\
|\sup_{h \in \mathcal{G}} \langle w, h \rangle_n| &\leq 
     | \sup_{h^L} \langle w, h_L \rangle_n | + \sigma \sqrt{2 \log \frac{2n}{\delta}} (\epsilon + \epsilon_{n, 2\delta}) \\
   &\leq   sB \sigma \sqrt{ 2 \frac{ \log N_{[]} + \log \frac{1}{\delta}}{n}} + \sigma \sqrt{2 \log \frac{2n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
   &\leq  sB \sigma \sqrt{ 2 \frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
   \sigma \sqrt{ 2\log \frac{2n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
   &\leq sB \sigma \sqrt{ 2\frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
   \sigma\sqrt{2 \log \frac{2n}{\delta}} \epsilon + sB \sigma \sqrt{2 \frac{sK^{**} (2sbB)^{1/2} + \log \frac{1}{\delta}}{n \epsilon^{1/2}} \log \frac{2n}{\delta}} \\
   &\leq \sigma\sqrt{2\log \frac{2n}{\delta}} \epsilon + 2 sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} \log^2 \frac{2n}{\delta}}{n \epsilon^{1/2}}} \\
\end{align*}

>>>>

The middle term can be bounded with the assumption that $\|f^*_k - \bar{f}^*_k \|_\infty \leq 2B$.

@@

Let us suppose condition~\ref{cond:simplify_covering_number} holds, then, by Corollary~\ref{cor:convexbracket_ln}, with probability at least $1-\delta$, each bracketing pair $(h_U, h_L)$ is close in $L_1(P_n)$ norm, i.e., for all $(h_U, h_L)$, 
$\frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i) | \leq 2 \epsilon + sB \sqrt{ \frac{sK^{**}(2sbB
)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. We verify at the end of the proof that condition~\ref{cond:simplify_covering_number} indeed holds.

@@

We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{ \frac{sK^{**}(2sbB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. Let $\mathcal{E}_{[\,]}$ denote the event that for each $h \in \mathcal{G}$, there exists $h_L$ in the $\epsilon$-bracketing such that $\|h-h_L\|_{L_{P_n}} \leq 2\epsilon + \epsilon_{n, \delta}$. $\mathcal{E}_{[\,]}$ has probability at most $1-\delta$ as shown.\\

Let $\mathcal{E}_{\|w\|_\infty}$ denote the event that $\| w \|_\infty \leq \sigma \sqrt{ 2\log \frac{2n}{\delta}}$; $\mathcal{E}_{\|w\|_\infty}$ has probability at most $1-\delta$. We take an union bound between $\mathcal{E}_{\|w\|_\infty}$ and $\mathcal{E}_{[\,]}$ and get that, with probability at most $1-2\delta$, for all $h$:
\[
|\langle w, h - h_L\rangle_n| \leq \| w \|_\infty \frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq
  \sigma \sqrt{2 \log \frac{4n}{\delta}} \left( \epsilon + \epsilon_{n,2\delta} \right)
\]

Because $w$ is a subgaussian random variables, for any fixed vector $h_L = (h_L(X_1),...,h_L(X_n))$, with probability at least $1-\delta$, $|\langle w, h_L \rangle_n | \leq \| h_L \|_n \sigma \sqrt{ \frac{2}{n} \log \frac{2}{\delta} }$. Using union bound again, we have that the event $\sup_{h_L} |\langle w, h_L \rangle| \leq sB \sigma \sqrt{ \frac{2}{n}\log \frac{2 N_{[]}}{\delta}}$ has probability at most $1-\delta$.

Putting this together, we have that
\begin{align*}
|\langle w, h \rangle_n | &\leq | \langle w, h_L\rangle_n| + |\langle w, h - h_L\rangle_n|\\
|\sup_{h \in \mathcal{G}} \langle w, h \rangle_n| &\leq 
     | \sup_{h^L} \langle w, h_L \rangle_n | + \sigma \sqrt{2 \log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, 2\delta}) \\
   &\leq   sB \sigma \sqrt{ 2 \frac{ \log N_{[]} + \log \frac{1}{\delta}}{n}} + \sigma \sqrt{2 \log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, \delta}) \\
   &\leq  sB \sigma \sqrt{ 2 \frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
   \sigma \sqrt{ 2\log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, \delta}) \\
   &\leq sB \sigma \sqrt{ 2\frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
   2\sigma\sqrt{2 \log \frac{2n}{\delta}} \epsilon + sB \sigma \sqrt{2 \frac{sK^{**} (2sbB)^{1/2}\log \frac{1}{\delta}}{n \epsilon^{1/2}} \log \frac{2n}{\delta}} \\
   &\leq 2\sigma\sqrt{2\log \frac{2n}{\delta}} \epsilon + 2 sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} \log^2 \frac{2n}{\delta}}{n \epsilon^{1/2}}} \\
\end{align*}
